An Evolutionary Quantitative Genetic Model of the Negative Selection Process in Humans

### 2023-07-01 manuscript/manuscript.tex
more methods

Given the accuracy of the SC16 model in predicting the reduction factor $B$ and
ratchet rate for a single segment under general mutation-selection processes,
we extended their model so that it could be applied to whole-genome data. Our
software method \texttt{bgspy} calculates the equilibrium additive genic
fitness variance ($V_a$) and ratchet rate ($R$) across grids of mutation rates
and selection coefficients for each pre-specified segment in the genome that
may be under negative selection (e.g. coding sequences or UTRs). Then, our
method computes a reduction map $B(x)$ for each position $x$ in the genome,
which is determined by the fitness variation at each segment and their spacing
along the user-supplied recombination map (see Methods XXX). To distinguish
between McVicker's B maps based on classic BGS theory, we call our reduction
map $B(x)$ a B' map.

@@

>>>>

Given the accuracy of the SC16 model in predicting the reduction factor $B$ and
ratchet rate for a single segment under general mutation-selection processes,
we extended their model so that it could be applied to whole-genome data. Our
software method \texttt{bgspy} numerically solves Equations XXX to compute the
equilibrium additive genic fitness variance ($V_a$) and ratchet rate ($R$)
across grids of mutation rates and selection coefficients. This is done for
each pre-specified segment in the genome that may be under negative selection
(e.g. coding sequences or UTRs). Then, these equilibrium can be used to
calculate a reduction map $B(x)$ across genomic positions $x$. To distinguish
between McVicker's B maps based on classic BGS theory, we call our reduction
map $B(x)$ a B' map.

@@

Ipsita Agarwal article

what time scale is the average mutation being lost at?
